% Created 2016-08-18 Thu 23:36
\documentclass[10pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{fixltx2e}
\usepackage{graphicx}
\usepackage{grffile}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\usepackage{geometry}\geometry{verbose,tmargin=1in,bmargin=1in,lmargin=1.2in,rmargin=1.2in}
\usepackage[stretch=10,babel=true]{microtype}\usepackage{lmodern}
\setlength\parindent{0pt}\linespread{0.95}
%\author{Jonghyun Yun}
\date{}
\title{MATH 5312: Mathematical Statistics I\\\medskip
\large Fall 2016}
\hypersetup{
 pdfauthor={Jonghyun Yun},
 pdftitle={MATH 5312: Mathematical Statistics I},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 25.0.94.2 (Org mode 8.3.5)}, 
 pdflang={}}
\begin{document}

\maketitle
%\setcounter{tocdepth}{3}
%\tableofcontents


\section*{Course Information}
\label{sec:orgheadline4}
\begin{itemize}
\item Instructor: Jonghyun Yun
\item Office Telephone Number:
\item Email Address: "jyun" at-sign "utep" dot "edu"

\item Course Webpage: \url{http://wweb.uta.edu/faculty/yun}
\item Office Hours: PKH 446, Tu/Thu 2:00-3:00 pm and by appointment

\item Section Information: MATH 5312: Mathematical Statistics I
\item Time and Place of Class Meetings: PKH 302, Tu/Thu 11:00- 12:20 pm
\item Telephone: 272-1148
\item Prerequisite: MATH 5307 or concurrent registration or consent of instructor.
\item Required Textbooks
\begin{itemize}
\item Hogg, R. V., McKean, J. W. and Craig, A. T. \emph{Introduction to Mathematical Statistics}. 7th Edition. Boston: Pearson, 2013. ISBN-10: 0-321-79543-1, ISBN-13: 978-0-321-79543-4
\item Other Recommended Textbooks and Resources
\begin{itemize}
\item Marden J. I. Mathematical Statistics Old School. 2012. \href{http://www.istics.net/pdfs/mathstat.pdf}{\url{http://www.istics.net/pdfs/mathstat.pdf}}
\end{itemize}
\end{itemize}
\end{itemize}
\subsection*{Course Content}
\label{sec:orgheadline1}
This course is a calculus-based introduction to the concepts of mathematical statistics.
We will cover selected portions of Chapters I-V of the textbook (HMC), with main focus on topics including but not limited to: Probability, conditional probability, random variables, distribution and density functions, joint and conditional distributions, various families of discrete and continuous distributions, moment generating functions (MGF), MGF technique for sums, convergence in distribution, convergence in probability, central limit theorem.

\subsection*{Student Learning Outcomes}
\label{sec:orgheadline2}
Goals for this course include developing critical thinking skills, and the abilities to apply techniques of calculus (i.e., derivatives, integration, etc.) to understand basic concepts in probability and foundations of statistical inference.
\subsection*{Important dates}
\label{sec:orgheadline3}
\begin{itemize}
\item 9/12/16: Census date
\item 9/22/16: Midterm 1
\item 10/20/16: Midterm 2
\item 11/2/16: Last day to drop classes
\item 11/22/16: Midterm 3
\item TBA: Final exam
\end{itemize}
\section*{Grading}
\label{sec:orgheadline8}
The usual grading scale will be used for this course.
\begin{table}[htb]
\centering
\begin{tabular}{ccccc}
A & B & C & D & F\\
\hline
100-90 & 89-80 & 79-70 & 69-60 & below 60\\
\end{tabular}
\end{table}

\subsection*{Grade Distribution}
\label{sec:orgheadline5}
\begin{itemize}
\item 25\% Homework Assignments
\item 50\% Midterm Exams
\item 25\% Final Exam
\end{itemize}
\subsection*{Homework}
\label{sec:orgheadline6}
Homework must be printed out and submitted in class. The instructors will not be
able to print out e-mailed or online-only assignment submissions. Late coursework will not be accepted without a university approved excuse.
It is imperative that you show all your work; simply stating an answer will result in no credit for the problem. 
\subsection*{Exams}
\label{sec:orgheadline7}
Exams will be closed book, open calculators. Calculators may not be shared on exams. Cell phone calculators are not permitted on exams.
A single page (on US letter size paper), hand-written cheat-sheet is permitted for each exam.
Make-up exams will only be given in rare cases. Students are expected to take the exam at the
scheduled times.

\section*{Lecture Attendance}
\label{sec:orgheadline9}
At the University of Texas at Arlington, taking attendance is not required. Rather, each
faculty member is free to develop his or her own methods of evaluating students’ academic performance,
which includes establishing course-specific policies on attendance. As the instructor of this section, I strongly
encourage you to attend all lectures. You are responsible for any and all announcements made in class. You are
also responsible for any material missed during class.
\section*{Drop Policy}
\label{sec:orgheadline10}
Students may drop or swap (adding and dropping a class concurrently) classes through selfservice
in MyMav from the beginning of the registration period through the late registration period. After the
late registration period, students must see their academic advisor to drop a class or withdraw. Undeclared
students must see an advisor in the University Advising Center. Drops can continue through a point two-thirds
of the way through the term or session. It is the student's responsibility to officially withdraw if they do not
plan to attend after registering. Students will not be automatically dropped for non-attendance. Repayment
of certain types of financial aid administered through the University may be required as the result of dropping
classes or withdrawing. For more information, contact the Office of Financial Aid and Scholarships
(\url{http://wweb.uta.edu/aao/fao/}).
\section*{Academic Integrity}
\label{sec:orgheadline11}
Students enrolled in this course are expected to adhere to the UT Arlington Honor Code:
\begin{quote}
I pledge, on my honor, to uphold UT Arlington’s tradition of academic integrity, a tradition that
values hard work and honest effort in the pursuit of academic excellence.

I promise that I will submit only work that I personally create or contribute to group
collaborations, and I will appropriately reference any work from other sources. I will follow the
highest standards of integrity and uphold the spirit of the Honor Code.
\end{quote}
UT Arlington faculty members may employ the Honor Code as they see fit in their courses, including (but not
limited to) having students acknowledge the honor code as part of an examination or requiring students to
incorporate the honor code into any work submitted. Per UT System Regents’ Rule 50101, §2.2, suspected
violations of university’s standards for academic integrity (including the Honor Code) will be referred to the
Office of Student Conduct. Violators will be disciplined in accordance with University policy, which may
result in the student’s suspension or expulsion from the University.
\section*{Americans with Disabilities Act}
\label{sec:orgheadline12}
UT Arlington is on record as being committed to both the spirit and letter of all federal equal opportunity legislation, including The Americans with Disabilities Act (ADA), The Americans with Disabilities Amendments Act (ADAAA), and Section 504 of the Rehabilitation Act. 
All instructors at UT Arlington are required by law to provide "reasonable accommodations" to
students with disabilities, so as not to discriminate on the basis of that disability. 
Students are responsible for providing the instructor with official notification in the form of a letter certified by the Office for Students with Disabilities. Students experiencing a range of conditions (Physical, Learning, Chronic Health, Mental Health, and Sensory) that may cause diminished academic performance or other barriers to learning may seek services and/or accommodations by contacting: 
\begin{itemize}
\item Office for Students with Disabilities (OSD): \url{http://www.uta.edu/disability} or 817-272-3364.
\item Counseling and Psychological Services (CAPS): \url{http://www.uta.edu/caps} or 817-272-3671.
\end{itemize}
Only those students who
have officially documented a need for an accommodation will have their request honored. Information
regarding diagnostic criteria and policies for obtaining disability-based academic accommodations can be
found at \url{http://www.uta.edu/disability} or by calling the Office for Students with Disabilities at (817) 272-3364.
\section*{Title IX}
\label{sec:orgheadline13}
The University of Texas at Arlington is committed to upholding U.S. Federal Law “Title IX” such that no
member of the UT Arlington community shall, on the basis of sex, be excluded from participation in, be denied the
benefits of, or be subjected to discrimination under any education program or activity. For more information, visit \href{http://www.uta.edu/titleix/}{\url{http://www.uta.edu/titleix/}}.
\section*{Electronic Communication}
\label{sec:orgheadline14}
UT Arlington has adopted MavMail as its official means to communicate with
students about important deadlines and events, as well as to transact university-related business regarding
financial aid, tuition, grades, graduation, etc. All students are assigned a MavMail account and are responsible
for checking the inbox regularly. There is no additional charge to students for using this account, which
remains active even after graduation. Information about activating and using MavMail is available at
\url{http://www.uta.edu/oit/cs/email/mavmail.php}.
\section*{Student Feedback Survey}
\label{sec:orgheadline15}
At the end of each term, students enrolled in classes categorized as “lecture,”
“seminar,” or “laboratory” shall be directed to complete an online Student Feedback Survey (SFS).
Instructions on how to access the SFS for this course will be sent directly to each student through MavMail
approximately 10 days before the end of the term. Each student’s feedback enters the SFS database
anonymously and is aggregated with that of other students enrolled in the course. UT Arlington’s effort to
solicit, gather, tabulate, and publish student feedback is required by state law; students are strongly urged to
participate. For more information, visit \url{http://www.uta.edu/sfs}.
\section*{Final Review Week}
\label{sec:orgheadline16}
A period of five class days prior to the first day of final examinations in the long
sessions shall be designated as Final Review Week. The purpose of this week is to allow students sufficient
time to prepare for final examinations. During this week, there shall be no scheduled activities such as required
field trips or performances; and no instructor shall assign any themes, research problems or exercises of similar
scope that have a completion date during or following this week unless specified in the class syllabus. During
Final Review Week, an instructor shall not give any examinations constituting 10\% or more of the final grade,
except makeup tests and laboratory examinations. In addition, no instructor shall give any portion of the final
examination during Final Review Week. During this week, classes are held as scheduled. In addition,
instructors are not required to limit content to topics that have been previously covered; they may introduce
new concepts as appropriate.
\section*{Emergency Exit Procedures}
\label{sec:orgheadline17}
Should we experience an emergency event that requires us to vacate the
building, students should exit the room and move toward the nearest exit. When exiting the building during an
emergency, one should never take an elevator but should use the stairwells. Faculty members and instructional
staff will assist students in selecting the safest route for evacuation and will make arrangements to assist
handicapped individuals.
\section*{Student Support Services}
\label{sec:orgheadline18}
UT Arlington provides a variety of resources and programs designed to help
students develop academic skills, deal with personal situations, and better understand concepts and information
related to their courses. Resources include tutoring, major-based learning centers, developmental education,
advising and mentoring, personal counseling, and federally funded programs. For individualized referrals,
students may visit the reception desk at University College (Ransom Hall), call the Maverick Resource Hotline
at (817) 272-6107, send a message to \href{mailto:resources@uta.edu}{resources@uta.edu}, or view the information at \href{http://www.uta.edu/resources}{\url{http://www.uta.edu/resources}}.
\end{document}